\begin{song}{Five Years}{
	
	\chordset[Verse]{ \GMaj \Em \AMaj \CMajBassG }

	\chordset[Bridge]{ \Am \CMajBassG \GMaj \DSeven}
	
}

\begin{songverse}

\ch{G}Pushing through the market square

\ch{Em}So many mothers sighing.

\ch{A}News had just come over,

We had \ch{C/G}five years left to cry in.


\ch{G}News guy wept and told us 

\ch{Em}Earth was really dying.

\ch{A}Cried so much his face was wet

Then I \ch{C/G}knew he was not lying.

\end{songverse}

\begin{songverse}

I heard \ch{G}telephones, opera house, favorite melodies,

I saw \ch{Em}boys, toys, electric irons and TV's.

My \ch{A}brain hurt like a warehouse, it had no room to spare.               
 
I had to \ch{C/G}cram so many things to store everything in there

\end{songverse}

\begin{songverse}

And all the fat-skinny \mbox{\ch{Am}people, \quad \ch{C/G}}

And all the tall-short \ch{Am}people,\quad \ch{C/G}

And all the nobody \ch{G}people, \quad \ch{C/G}
                      
And all the somebody \ch{D\up{7}}people.

I never thought I'd need so many \ch{Am}people \quad \ch{C/G}

\end{songverse}

\begin{songverse}                                 
 \ch{G}A girl my age went off her head,
 
 \ch{Em}Hit some tiny children.
 
 If the \ch{A}black hadn't a-pulled her off,
 
 I think \ch{C/G}she would have killed them.
 
 \end{songverse}
 
 \begin{songverse}
                                          
 \ch{G}A soldier with a broken arm, 
 
 \ch{Em}Fixed his stare to the wheels of a Cadillac.
 
                                         
 A \ch{A}cop knelt and kissed the feet of a priest,
 
 And a \ch{C/G}queer threw up at the sight of that.
 
                                          
 \ch{G}I think I saw you in an ice-cream parlor,
 
 \ch{Em}Drinking milk shakes cold and long,
 
                                           
 \ch{A}Smiling and waving and looking so fine,
  
 \ch{C/G}Don't think you knew you were in this song.
 
 \end{songverse}
 
 \begin{songverse}
                          
 And it was \ch{G}cold and it rained so I felt like an actor
 
 And I \ch{Em}thought of Ma and I wanted to get back there,

 Your \ch{A}face, your race, the way that you talk,

 I \ch{C/G}kiss you, you're beautiful, I want you to walk!

 \end{songverse}
 
 \begin{songverse}

 We've got \ch{G}five years, stuck on my eyes,

 We've got \ch{Em}five years, what a surprise,

 We've got \ch{A}five years, my brain hurts a lot,

 We've got \ch{C/G}five years, that's all we've got.
 
\end{songverse}


\end{song}