\begin{song}{Pencil Skirt}{
	
	\git{Verse}

	\mbox{ \CMaj \AMaj \DMaj \GMaj }

	\git{Chorus}

	\mbox{ \EmShAm \CMajShE }
	
}

	 \begin{SongVerse}
		\ch{A}{Mis-shapes}, mistakes, misfits. 

		\ch{E}{Raised} on a diet of broken biscuits, oh \ch{F\#m}{}

		We don't look the same as you \ch{D}{}
		
		We don't do the things you do,
		
		But \ch{D7}{we} live around here too, oh really. 
	 \end{SongVerse}

	 \begin{SongVerse}
		\ch{A}{Mis-shapes}, mistakes, misfits,

		We'd \ch{E}{like} to go to town but we can't risk it, oh \ch{F\#m}{} 

		'Cos they just want to keep us out. \ch{D}{} 
		
		You could end up with a smack in the mouth

		\ch{D7}{Just} for standing out, now really.
	 \end{SongVerse}

	 \begin{SongVerse}

		\ch{A}{Brothers}, sisters, can't you \ch{E}{see?} 

		The future's owned by you and \ch{F\#m}{me}. 

		There won't be fighting in the \ch{D}{street}. 

		They think they've got us beat, 

		But \ch{D7}{revenge} is going to be so sweet. 
	\end{SongVerse}

	\begin{SongVerse}
		
		\ch{G}{}We're making a \ch{GMaj7}{move}, 

		we're making it \ch{G7}{now}. 

		We're coming out of the sidelines. 
		Just put your hands up - it's a raid yeah: 
		We want your homes, we want your lives, 
		we want the things you won't allow us. 
		We won't use guns, we won't use bombs
		We'll use the one thing we've got more of - that's our minds. 
		Check your lucky numbers, that much money could drag you under, oh. 
		What's the point of being rich if you can't think what to do with it? 
		'Cause you're so very thick. 
		Oh we weren't supposed to be, we learnt too much at school now 
		we can't help but see. 
		That the future that you've got mapped out is nothing much to shout about. 
		We're making a move, we're making it now,
		We're coming out of the side-lines. 
		Just put your hands up - it's a raid. 
		We want your homes, we want your lives,
		we want the things you won't allow us. 
		We won't use guns, we won't use bombs
		We'll use the one thing we've got more of - that's our minds. 
		Brothers, sisters, can't you see? 
		The future's owned by you and me. 
		There won't be fighting in the street. 
		They think they've got us beat but revenge is going to be so sweet. 
		We're making a move. We're making it now. 
		We're coming out of the sidelines. 
		Just put your hands up - it's a raid. 
		We want your homes, we want your lives, 
		we want the things you won't allow us. 
		We won't use guns, we won't use bombs
		We'll use the one thing we've got more of - that'sour minds. 
		And that's our minds. Yeah. 
	 \end{SongVerse}

\end{song}